---
title: "projet"
output: html_document
date: "2025-04-08"
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(scales)
library(shiny)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r}
# Chargement des données OWID
Covid19 <- read_delim("./owid-covid-data.csv", delim = ",") %>%
  filter(location %in% c("France", "Germany", "Italy")) %>%
  filter(!is.na(total_cases), !is.na(total_deaths)) %>%
  mutate(date = as.Date(date))

 

```
```{r}
# Graphique 1 : Cas cumulés
p1 <- ggplot(Covid19, aes(x = date, y = total_cases, color = location)) +
  geom_line(size = 1) +
  scale_y_log10(labels = comma) +
  labs(title = "Cas cumulés (échelle logarithmique)", x = "Date", y = "Total cas", color = "Pays") +
  theme_minimal(base_size = 14)

# Graphique 2 : Décès cumulés
p2 <- ggplot(Covid19, aes(x = date, y = total_deaths, color = location)) +
  geom_line(size = 1) +
  scale_y_log10(labels = comma) +
  labs(title = "Décès cumulés (échelle logarithmique)", x = "Date", y = "Total décès", color = "Pays") +
  theme_minimal(base_size = 14)

# Afficher les deux côte à côte
grid.arrange(p1, p2, ncol = 2)



```